Verifying Demonstrations

### 2018-11-14 paper/verifiability-analysis.tex
Edits eligibility verifiability in security analysis

As it is the case in the construction of blockchains, the hash value at the 
head depends on the previous blocks in the chain.
Thus, the predictability of \(t_s\) depends on the predictability of the blocks, which depends on the predictability of the transactions and the nonce needed by the miner.
In turn, the transactions depend on the signatures made by the signing keys 
corresponding to the used transactions --- which depends on uniformly random 
nonces.
If these were predictable, the adversary could conduct arbitrary transactions in the blockchain --- which is assumed to be hard by design.
Thus, Alice can predict \(t_s\) only with negligible probability, as \(t_s\) must have been published on the blockchain before being included in her proof share.

Also, the correctness of the challenge must be verifiable by any verifier 
(\(\TStime\)).

According to \cref{TemporallyRelated}, we must also prove that a proof share has not been created after a certain time.
Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
The hash values of the proof shares are committed to the blockchain, which means that there is a negligible probability that they were created after that.
Alice would have to choose a value \(y\) in the domain of the hash function \(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) is a valid proof.
If \(\Hash\) is collision resistant, finding \emph{any} preimage is hard.

>>>>

As it is the case in the construction of ledgers, the hash value of the head 
block depends on the previous blocks.
Thus, the predictability of \(t_s\) depends on the predictability of the 
blocks, which depends on the predictability of the transactions.
Assume that Alice can control all transactions going into a block.
This means that she must find a pre-image of the form of a valid block that is 
accepted by all nodes in the distributed ledger.
\Ie it depends on the pre-image resistance of the hash function used.
Thus, with a collision resistant hash function, Alice can predict \(t_s\) only 
with negligible probability; and it follows that, with high probability, 
\(t_s\) was published on the ledger before being included in her proof share.

The correctness of the challenge must be verifiable by any verifier 
(\(\TStime\)).
This can be done if the ledger is continuously extended at a fixed rate, \eg 
one new block every 10 minutes, as was the case for Bitcoin.

According to \cref{TemporallyRelated}, we must also prove that a proof share has not been created after a certain time.
Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
The hash values of the proof shares are committed to the ledger, which means 
that there is a negligible probability that they were created after that.
Alice is in the same situation as above:
she would have to choose a value \(y\) in the domain of the hash function 
\(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) 
is a valid proof for the desired protest, at the desired time.
If \(\Hash\) is collision resistant, finding \emph{any} pre-image is hard.
